Storm surge modelling in the Strait of Georgia

### 2014-11-20 RoughWork/manuscript.tex
Added dec2012 figures to text
Added observed residual to plot

%\subsection{High Resolution Atmospheric Forcing: Dec 17, 2012}

@@

Since the Strait of Georgia is a large, semi-enclosed body of water storm surges can behave and evolve differently than in other coastal regions. For instance, the complicated coastlines and local wind patterns result in important spatial variations in the surge amplitude. As such, strong winds caused by a large storm is not the only factor to be considered in community preparedness for surge conditions. The geometry of the Strait and local wind patterns render communities on the mainland side of the southern Strait of Georgia more susceptible to surges. Additionally, commmunities such as Campbell River are at risk due to the long fetch and predominately southerly winds during the winter months.

@@

%future directions: running real time, biology and chemistry, model improvements?
%comments on wetting and drying (maybe most important in shallow regions)
%summary of skill scores

>>>>

\subsection{High Resolution Atmospheric Forcing}

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/dec2012_surge.pdf}
\caption{Comparison modelled residuals using a low resolution and high resolution atmospheric product during the Dec 2012 storm surge simulation. }
\label{fig:dec2012_surge}
\end{figure}
%Add in observations?

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/dec2012_weather.pdf}
\caption{Comparison observed and modelled winds during Dec 2012 storm surge simulation at Point Atkinson and Sandheads.}
\label{fig:dec2013_weather}
\end{figure}

@@

Since the Strait of Georgia is a large, semi-enclosed body of water storm surges can behave and evolve differently than in other coastal regions. For instance, the complicated coastlines and local wind patterns result in important spatial variations in the surge amplitude. As such, the strong wind caused by a large storm are not the only factors to be considered in community preparedness for surge conditions. The geometry of the Strait and local wind patterns render communities on the mainland side of the southern Strait of Georgia more susceptible to surges. Additionally, commmunities such as Campbell River are at risk due to the long fetch and predominately southerly winds during the winter months.

@@

%future directions: running real time, biology and chemistry, model improvements?
%summary of skill scores
